Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-27 src/tex/ms.tex
merging correctly

In this work, we use the mismatch to quantify the accuracy of the waveform model. 
A natural extension of this work to investigate how the recalibration process affects
downstream analyses such as parameter estimation and population modeling.
Differentiable samplers such as~\citep{Wong:2022xvh}, which have been recently
introduced to the community, potentially allow one to optimize the waveform directly
using metrics from parameter estimation. For example, minimizing the bias in an injection-recovery run
could be used as a loss function. Overall, this approach could help reduce systematic waveform error
in parameter estimation simply through recalibrated waveforms. We plan to investigate these avenues in
the future.

>>>>

In this work, we use the mismatch to quantify the accuracy of the waveform model. 
A natural extension of this work is to investigate how the recalibration process affects
downstream analyses such as parameter estimation and population modeling.
Differentiable samplers such as~\citep{Wong:2022xvh}, which have been recently
introduced to the community, potentially allow one to optimize the waveform directly
using metrics from parameter estimation. For example, minimizing the bias in an injection-recovery run
could be used as a loss function. Overall, this approach could help reduce systematic waveform error
in parameter estimation simply through recalibrated waveforms. We plan to investigate these avenues in
the future.
